\MakeUppercase{Measuring polygonal niceness} \thanks{ This paper constitutes the completion of the final project for AMS 545 ``Computational Geometry''. }

### 2018-05-04 paper/main.tex
Stray typos

\newcommand{\RR}{\mathbb{R}}
\newcommand{\PP}{\mathcal{P}}
\newcommand{\EE}{\mathcal{E}}
\newcommand{\set}[1]{\{#1\}}
\newcommand{\norm}[1]{\|#1\|}
\newcommand{\abs}[1]{|#1|}
\newcommand{\chordarc}{{s_{\abs{\partial~\cdot~}}}}
\DeclareMathOperator{\diam}{\mathrm{diam}}
\DeclareMathOperator{\conv}{\mathcal{}}

@@

In principal of computing the $\alpha$ and chord-$f$ scores relies on sweeping
the continuum of points of $P$ and evaluating the aforementioned measurements.
To estimate this process in practice, we employ the following discretizing
scheme. Let $P$ be determined by the vertices $[v_1, \dots, v_n]$ given in
counterclockwise order. Then, given $\delta > 0$, loop through the vertices of
$P$, checking if $\norm{v_{i+1} - v_i} > \delta$. In the case where this holds,
we insert $v_i' = \frac{v_i + v_{i+1}}{2}$ after $v_i$ into the polygon and
resume the loop. This ensures that for any two adjacent vertices $v_{i}$ and
$v_{i+1}$ in the representation of $P$ we have $\norm{v_{i+1} - v_i} \leq
\delta$. As $\delta \to 0$ this estimates $\partial P$ more exactly. All
computations are done with respect to the $L_{\infty}$ norm. The implementation
of this procedure is given in Algorithm \ref{alg:delta}.

@@

\begin{figure}[t]
  \centering
  \begin{tabular}{lrrrrrrrrrr}
    \toprule
    $\delta$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
    \midrule
    0.05 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.15 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.26 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.36 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.47 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.57 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.68 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.78 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.89 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    1    &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    \bottomrule
  \end{tabular}
  \caption{%
    Effect of sweeping $\delta$ on measurements of $\alpha$-score on
    10 randomly generated polygons with 10 vertices in $[0,1]^2$.
    Unsurprisingly, the refinement of the different polygons has no effect on
    the $\alpha$-fatness score, since it introduces no additional area to the
    polygon and since the ``corners'' are already present.
  }
  \label{fig:delta-alpha}
\end{figure}

\begin{figure}[t]
  \centering
  \begin{tabular}{lrrrrrrrrrr}
    \toprule
    $\delta$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
    \midrule
    0.05  &  0.83 &  0.46 &  0.83 &  0.89 &  0.54 &  0.67 &  0.62 &  1.00 &  0.86 &  0.55 \\
    0.15  &  0.79 &  0.90 &  0.72 &  0.60 &  0.90 &  0.67 &  0.99 &  0.83 &  0.66 &  0.90 \\
    0.26  &  1.00 &  0.75 &  0.50 &  0.60 &  0.90 &  0.49 &  0.77 &  0.52 &  0.72 &  0.69 \\
    0.36  &  0.89 &  1.00 &  0.50 &  0.60 &  0.52 &  0.49 &  1.00 &  0.92 &  0.74 &  0.51 \\
    0.47  &  0.61 &  1.00 &  0.50 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
    0.57  &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
    0.68  &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
    0.78  &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
    0.89  &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
    1     &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  1.00 &  1.00 &  0.62 &  1.00 &  0.51 \\
    \bottomrule
  \end{tabular}
  \caption{%
    Effect of sweeping $\delta$ on measurements of ${\chordarc}_\infty$ on
    10 randomly generated polygons with 10 vertices in $[0,1]^2$. The overall behavior is
    difficult to summarize.  Though one might hope that as $\delta \to 0$ we see
    a stabilization in the chard arc score, this does not appear to occur.
    Moreover, there does not seem to be even a monotonic evolution in the score
    as $\delta \to 0$. This is likely due to the fact that smaller values of
    $\delta$ permit stranger nonconvexities to emerge as viable chords.
  }
  \label{fig:delta-arc}
\end{figure}

>>>>

\newcommand{\RR}{\mathbb{R}}
\newcommand{\PP}{\mathcal{P}}
\newcommand{\EE}{\mathcal{E}}
\newcommand{\set}[1]{\{#1\}}
\newcommand{\norm}[1]{\|#1\|}
\newcommand{\abs}[1]{|#1|}
\newcommand{\chordarc}{{s_{\textrm{arc}}}}
\DeclareMathOperator{\diam}{\mathrm{diam}}
\DeclareMathOperator{\conv}{\mathcal{CH}}

@@

In principal computing the $\alpha$-fatness and chord-$f$ scores relies on sweeping
the continuum of points of $P$ and evaluating the aforementioned measurements.
To estimate this process in practice, we employ the following discretizing
scheme. Let $P$ be determined by the vertices $[v_1, \dots, v_n]$ given in
counterclockwise order. Then, given $\delta > 0$, loop through the vertices of
$P$, checking if $\norm{v_{i+1} - v_i} > \delta$. In the case where this holds,
we insert $v_i' = \frac{v_i + v_{i+1}}{2}$ after $v_i$ into the polygon and
resume the loop. This ensures that for any two adjacent vertices $v_{i}$ and
$v_{i+1}$ in the representation of $P$ we have $\norm{v_{i+1} - v_i} \leq
\delta$. As $\delta \to 0$ this estimates $\partial P$ more exactly. All
computations are done with respect to the $L_{\infty}$ norm. The implementation
of this procedure is given in Algorithm \ref{alg:delta}.

@@

\begin{figure}[t]
  \centering
  \begin{tabular}{lrrrrrrrrrr}
    \toprule
    $\delta$ & $P_1$ & $P_2$ & $P_3$ & $P_4$ & $P_5$ & $P_6$ & $P_7$ & $P_8$ & $P_9$ & $P_{10}$ \\
    \midrule
    0.05 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.15 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.26 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.36 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.47 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.57 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.68 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.78 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    0.89 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    1    &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
    \bottomrule
  \end{tabular}
  \caption{%
    Effect of sweeping $\delta$ on measurements of $\alpha$-score on
    10 randomly generated polygons with 10 vertices in $[0,1]^2$.
    Unsurprisingly, the refinement of the different polygons has no effect on
    the $\alpha$-fatness score, since it introduces no additional area to the
    polygon and since the ``corners'' are already present.
  }
  \label{fig:delta-alpha}
\end{figure}

\begin{figure}[t]
  \centering
  \begin{tabular}{lrrrrrrrrrr}
    \toprule
    $\delta$ & $P_1$ & $P_2$ & $P_3$ & $P_4$ & $P_5$ & $P_6$ & $P_7$ & $P_8$ & $P_9$ & $P_{10}$ \\
    \midrule
    0.05  &  0.83 &  0.46 &  0.83 &  0.89 &  0.54 &  0.67 &  0.62 &  1.00 &  0.86 &  0.55 \\
    0.15  &  0.79 &  0.90 &  0.72 &  0.60 &  0.90 &  0.67 &  0.99 &  0.83 &  0.66 &  0.90 \\
    0.26  &  1.00 &  0.75 &  0.50 &  0.60 &  0.90 &  0.49 &  0.77 &  0.52 &  0.72 &  0.69 \\
    0.36  &  0.89 &  1.00 &  0.50 &  0.60 &  0.52 &  0.49 &  1.00 &  0.92 &  0.74 &  0.51 \\
    0.47  &  0.61 &  1.00 &  0.50 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
    0.57  &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
    0.68  &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
    0.78  &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
    0.89  &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
    1     &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  1.00 &  1.00 &  0.62 &  1.00 &  0.51 \\
    \bottomrule
  \end{tabular}
  \caption{%
    Effect of sweeping $\delta$ on measurements of ${\chordarc}_\infty$ on
    10 randomly generated polygons with 10 vertices in $[0,1]^2$. The overall behavior is
    difficult to summarize.  Though one might hope that as $\delta \to 0$ we see
    a stabilization in the chard arc score, this does not appear to occur.
    Moreover, there does not seem to be even a monotonic evolution in the score
    as $\delta \to 0$. This is likely due to the fact that smaller values of
    $\delta$ permit stranger nonconvexities to emerge as viable chords.
  }
  \label{fig:delta-arc}
\end{figure}
